---
title: "Homework 6"
author: "Ifrah Fayyaz"
date: "12/3/2021"
output: github_document
---

#### Loading required libraries:

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)
library(broom)
```

## Problem 1

```{r, message=FALSE, warning=FALSE}
prob1 = 
  read_csv("./data/birthweight.csv") %>%
  mutate(babysex = as.factor(babysex)) %>%
  mutate(frace = as.factor(frace)) %>%
  mutate(malform = as.factor(malform)) %>%
  mutate(mrace = as.factor(mrace)) %>%
  select(-pnumlbw, -pnumsga) #Getting rid of these two variables 
                             #as they have all values = 0

sum(is.na(prob1))
```

As the total number of missing values is ``r sum(is.na(prob1))``, we know that there are no missing values in the dataset.

#### Proposed Regression Analysis:

For the regression analysis, I will first check which variables show a crude associated with `birthweight` and then add them into a multivariable model to assess significant predictors of `birthweight`.

**Crude Analysis:**
<br>
We will run simple regression models, checking the associations between our outcome of interest `bwt` and all its potential predictors.

```{r, message=FALSE, warning=FALSE}
# For continuous variables, we can use the following code to check significant predictors:

sig_check1 = prob1 %>%
  select(-bwt, -mrace, -frace, -babysex) %>%  # exclude outcome and factor variables
  map(~lm(prob1$bwt ~ .x, data = prob1)) %>% 
  map(summary) %>% 
  map(c("coefficients")) %>% 
  map_dbl(8) %>%
  knitr::kable(digits = 2)
sig_check1

sig_check2 = prob1 %>%
  mutate(babysex = fct_infreq(babysex)) %>%
  lm(bwt ~ babysex, data = .) %>%
  broom::tidy() %>%
  select(term, p.value) %>%
  knitr::kable(digits = 2)
sig_check2

sig_check3 = prob1 %>%
  mutate(mrace = fct_infreq(mrace)) %>%
  lm(bwt ~ mrace, data = .) %>%
  broom::tidy() %>%
  select(term, p.value) %>%
  knitr::kable(digits = 2)
sig_check3

sig_check4 = prob1 %>%
  mutate(frace = fct_infreq(frace)) %>%
  lm(bwt ~ frace, data = .) %>%
  broom::tidy() %>%
  select(term, p.value) %>%
  knitr::kable(digits = 2)
sig_check4

```
*Description:*
<br>
From the analysis above, we see that all variables except `malform`, `menarche` and `parity` show significant crude associations with our outcome of interest `bwt`. We will be excluding these variables from the working dataset and run a multivariable regression model.

**Multivariable Analysis:**

```{r, message=FALSE, warning=FALSE}
prob1_reg = prob1 %>%
  select(-malform, -menarche, -parity, -wtgain) # we are getting rid of "wtgain" because we are getting a 
                                                # coefficient of NA for it - meaning it is linearly  
                                                # related with other variables in the model

reg_model = lm(bwt ~ ., data = prob1_reg) 

reg_model %>%
  broom::tidy() %>%
  select(term, estimate, p.value) %>%
  mutate(term = str_replace(term, "babysex2", "Female")) %>%
  mutate(term = str_replace(term, "frace2", "Father: Black")) %>%
  mutate(term = str_replace(term, "frace3", "Father: Asian")) %>%
  mutate(term = str_replace(term, "frace4", "Father: Puerto Rican")) %>%
  mutate(term = str_replace(term, "frace8", "Father: Other")) %>%
  mutate(term = str_replace(term, "mrace2", "Mother: Black")) %>%
  mutate(term = str_replace(term, "mrace3", "Mother: Asian")) %>%
  mutate(term = str_replace(term, "mrace4", "Mother: Puerto Rican")) %>%
  knitr::kable(digits = 2) 


```
*Description:*
<br>
From the multivariable analysis above, we see that the following variables are significant predictors of birthweight: 

- `babysex`: Baby's sex (Female babies significantly have higher birthweight as compared to male babies) <br>
- `bhead`: baby’s head circumference at birth (greater head circumference associated with higher birthweight) <br>
- `blength`: baby’s length at birth (greater length associated with higher birthweight) <br>
- `delwt`: mother’s weight at delivery (higher weight of the mother associated with higher birthweight) <br>
- `gaweeks`: gestational age in weeks (higher gestational age associated with higher birthweight) <br>
- `mrace`: mother’s race (Black mothers are significantly associated with having lower birthweight babies as compared to white) <br>
- `smoken`: average number of cigarettes smoked per day during pregnancy (greater number of cigarettes smoked associated with lower birthweight)


#### Model 1:

```{r, message=FALSE, warning=FALSE}
fit1 = lm(bwt ~ blength + gaweeks, data = prob1)

fit1 %>%
  broom::tidy() %>%
  select(term, estimate, p.value) %>%
  mutate(term = str_replace(term, "babysex2", "Female")) %>%
  knitr::kable(digits = 2) 
```


#### Model 2:

```{r, message=FALSE, warning=FALSE}
prob1 = prob1 %>%
  mutate(babysex = fct_infreq(babysex))

fit2 = lm(bwt ~ bhead * blength * babysex, data = prob1)

fit2 %>%
  broom::tidy() %>%
  select(term, estimate, p.value) %>%
  mutate(term = str_replace(term, "bhead", "Head Circumference (cm)")) %>%
  mutate(term = str_replace(term, "blength", "Baby's Length (cm)")) %>%
  mutate(term = str_replace(term, "babysex2", "Female")) %>%
  mutate(term = str_replace(term, ":", " x ")) %>%
  mutate(term = str_replace(term, ":", " x ")) %>%
  knitr::kable(digits = 2)
```

**Cross-Validation Between Models:**

```{r, message=FALSE, warning=FALSE, eval = FALSE}
cv_fit1 = 
  crossv_mc(prob1, 100)

cv_fit1 = 
  cv_fit1 %>% 
  mutate(
    my_mod  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + smoken, data = .x)),
    mod1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    mod2  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_my_mod = map2_dbl(my_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
    rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y)))

cv_fit1 %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```



```{r, message=FALSE, warning=FALSE}

```



```{r, message=FALSE, warning=FALSE}

```



```{r, message=FALSE, warning=FALSE}

```